%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Benjamin Johnston} \\ \vspace{1pt}
    \small Columbus, OH $|$ (614) 843-3974 $|$
    \href{mailto:bejaunst@gmail.com}{\underline{bejaunst@gmail.com}} $|$
    \href{https://linkedin.com/in/bejaunst}{\underline{linkedin.com/in/bejaunst}} $|$
    \href{https://github.com/cetio}{\underline{github.com/cetio}} $|$
    \href{https://cetio.github.io}{\underline{cetio.github.io}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Operations Engineer (RPA \& Model Evaluation)}{Nov 2025 -- Jun 2026}
      {Handshake --- Contract}{Remote}
      \resumeItemListStart
        \resumeItem{Cut manual annotation and triage effort by 95\% across 400+ contractor hours by building AutoHandshake!, a Selenium-driven automation suite with UI-stall recovery, multi-tab orchestration, and full audit trails.}
        \resumeItem{Evaluated 4,000+ multimodal AI responses against structured quality rubrics for correctness and reasoning, earning the Handshake Model Validation 2 --- Expert credential.}
        \resumeItem{Trained contractors on platform workflows and rubric interpretation, raising evaluation consistency team-wide.}
      \resumeItemListEnd

    \resumeSubheading
      {Expert Contributor}{Dec 2025 -- May 2026}
      {Snorkel AI --- Contract}{Remote}
      \resumeItemListStart
        \resumeItem{Shaped constraint-based training pipelines for Claude and ChatGPT across two contracted projects targeting complex programming and logic reasoning.}
        \resumeItem{Ran CI/CD validation in Docker to catch defects pre-release and protect training-set integrity.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Software Engineer}{Jul 2021 -- Present}
      {Independent client engagements}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered SDKs, automation tooling, and API integrations for individual clients, including an AI-assisted grading platform with LMS OAuth that reached \textasciitilde95\% grading accuracy and cut instructor workload in half.}
        \resumeItem{Eliminated a user-mode virtual-input layer from a device-integration pipeline, removing its overhead from the execution path entirely.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Selenium} $|$ \emph{D} $|$ \href{https://www.github.com/cetio/selenium}{\underline{github.com/cetio/selenium}}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Authored the only Selenium WebDriver client for D: comprehensive, fully documented, and W3C-compliant, with typed APIs, driver auto-detection, and full session lifecycle management.}
            \resumeItem{Powers real automation workloads, including AutoHandshake!, with production-grade coverage across clicks, input, forms, and JavaScript execution.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Intuit} $|$ \emph{D} $|$ \href{https://github.com/cetio/intuit}{\underline{github.com/cetio/intuit}}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Designed a Pydantic-inspired LLM SDK mapping chat completions, structured output, streaming, and tool calls onto native D types, avoiding a new stack syntax to learn.}
            \resumeItem{Supports OpenAI, Claude, Qwen, OpenRouter, and local models through one extensible routing layer.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Google-SDK} $|$ \emph{D} $|$ \href{https://github.com/cetio/google-sdk}{\underline{github.com/cetio/google-sdk}}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Unified Drive, Docs, Sheets, and Gmail access behind one client with OAuth session handling and typed errors for auth, permission, and rate-limit failures.}
            \resumeItem{Automated MIME detection and native Docs/Sheets export, removing boilerplate from Google API integrations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Insurgent: Client} $|$ \emph{D, JavaScript}}{2026 -- Present}
          \resumeItemListStart
            \resumeItem{Built a real-time companion client rendering 10,000+ map tiles and 5,000+ units through live WebSocket feeds in under a second.}
            \resumeItem{Combined Selenium-driven data capture with a responsive live dashboard as a solo-developed, full-stack system.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, D, Python, Ruby, JavaScript, SQL, C, C++, x86 Assembly} \\
     \textbf{Automation \& Quality}{: Selenium, WebDriver, browser automation, test design, CI/CD, Docker, structured evaluation, audit trails, failure recovery} \\
     \textbf{Software Engineering}{: REST APIs, OAuth 2.0, SDK design, WebSockets, HTML parsing, JSON Schema, LLM integration, Git, CMake, Linux}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus State Community College}{Expected Dec 2026}
      {AAS, Software Development}{Columbus, OH}
  \resumeSubHeadingListEnd

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certifications}{: Handshake Model Validation 2 --- Expert (AI response evaluation across 4,000+ multimodal samples)}
    }}
 \end{itemize}

\end{document}
