%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Benjamin Johnston} \\ \vspace{1pt}
    \small (614) 843-3974 $|$
    \href{mailto:bejaunst@gmail.com}{\underline{bejaunst@gmail.com}} $|$
    \href{https://linkedin.com/in/bejaunst}{\underline{linkedin.com/in/bejaunst}} $|$
    \href{https://github.com/cetio}{\underline{github.com/cetio}} $|$
    \href{https://cetio.github.io}{\underline{cetio.github.io}}
\end{center}\vspace{-6pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Ruby, JavaScript, TypeScript, D, C\#, C, C++, SQL, x86 Assembly} \\
     \textbf{Automation \& Quality}{: Selenium, WebDriver, test architecture, CI/CD, Docker, structured evaluation, audit trails, failure recovery} \\
     \textbf{Software Engineering}{: REST APIs, OAuth 2.0, SDK design, WebSockets, JSON Schema, LLM integration, Git, CMake, Linux}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Operations Engineer (Automation \& Model Evaluation)}{Nov 2025 -- Jun 2026}
      {Handshake --- Contract}{}
      \resumeItemListStart
        \resumeItem{Cut manual annotation and triage effort by 95\% by building AutoHandshake!, a Ruby/JavaScript Selenium automation suite with UI-stall recovery, multi-tab orchestration, and full audit trails.}
        \resumeItem{Evaluated 4,000+ multimodal AI responses using rubric-based scoring for correctness and reasoning quality, holding the Handshake Model Validation 2 --- Expert credential.}
        \resumeItem{Mentored contractors on platform workflows and rubric interpretation, raising evaluation consistency team-wide.}
      \resumeItemListEnd

    \resumeSubheading
      {Expert Contributor}{Dec 2025 -- May 2026}
      {Snorkel AI --- Part-time Contract}{}
      \resumeItemListStart
        \resumeItem{Engineered constraint-based training workflows for Claude and ChatGPT across 2 contracted projects targeting complex programming and logic reasoning tasks.}
        \resumeItem{Validated training-set integrity through Docker-based CI/CD, catching defects pre-release.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Selenium} $|$ \emph{D} $|$ \href{https://github.com/cetio/selenium}{\underline{github.com/cetio/selenium}}}{}
          \resumeItemListStart
            \resumeItem{Authored the only maintained W3C-compliant Selenium WebDriver client for D (4,800+ lines), with typed APIs, driver auto-detection for 4 browsers, and full session lifecycle management.}
            \resumeItem{Published on the DUB package registry with Selenium Grid support; powers live data capture in the Insurgent companion system.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Intuit} $|$ \emph{D} $|$ \href{https://github.com/cetio/intuit}{\underline{github.com/cetio/intuit}}}{}
          \resumeItemListStart
            \resumeItem{Authored the first native LLM SDK for D (8,400+ lines), mapping chat completions, structured output, SSE streaming, and tool calls onto typed D structures.}
            \resumeItem{Supports OpenAI, Claude, and Qwen with OpenAI-compatible routing for OpenRouter and local models, plus SIMD-accelerated embeddings.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Google-SDK} $|$ \emph{D} $|$ \href{https://github.com/cetio/google-sdk}{\underline{github.com/cetio/google-sdk}}}{}
          \resumeItemListStart
            \resumeItem{Authored a minimal-boilerplate Google SDK for D covering 4 services (Drive, Docs, Sheets, Gmail) across 4,100+ lines, with 2 OAuth identity layers and a 5-category typed error taxonomy.}
            \resumeItem{Automated MIME detection and native Docs/Sheets export, built on a custom OAuth 2.0 library with PKCE, token caching, and revocation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Insurgent: Client} $|$ \emph{D, JavaScript}}{}
          \resumeItemListStart
            \resumeItem{Solo-developed a 3-component companion system (8,400+ lines) rendering 10,000+ tiles, 5,000+ units, 2,000+ research trees, and 8,000+ images via WebSocket feeds in under a second.}
            \resumeItem{Combined Selenium-driven data capture with filesystem-cached match state, live dashboards, and authentication across all three components.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus State Community College}{Expected Dec 2026}
      {AAS, Software Development}{}
  \resumeSubHeadingListEnd
\vspace{-8pt}

%-----------FREELANCE EXPERIENCE-----------
\section{Freelance Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freelance Software Engineer}{}
      {Independent client engagements}{}
      \resumeItemListStart
        \resumeItem{Delivered SDKs, automation tooling, and API integrations for individual clients, including an AI-assisted grading platform with LMS OAuth that reached $\sim$95\% grading accuracy and cut instructor workload in half.}
        \resumeItem{Eliminated a user-mode virtual-input layer from a device-integration pipeline, reducing its overhead by 100\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
